\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-27 metatheory-condensed.tex
Tarski-style universes

\cref{fig:typing-selected} presents selected syntax and typing rules of \TT.
The new forms (relative to MLTT) are highlighted.
We briefly review the base MLTT fragment first.

@@

%Note that we are actually using predicative universe, so we actually have different levels of universes $\cU_i$. 
%We omit universe levels in our latex presentation for conciseness and readability.

>>>>

\cref{fig:typing-selected} presents the syntax and selected typing rules of \TT.
The new forms (relative to MLTT) are highlighted.
We briefly review the base MLTT fragment first.

@@

We use Tarski-style universes~\cite{hofmann1997syntax}: a universe~$\cU$
is inhabited by the \emph{codes} of types, with $\El{t}$ decoding~$t$ and
$\codety{T}$ encoding type~$T$ (rules \ruleref{ty/el} and \ruleref{tm/c}).
MLTT has an infinite hierarchy of universes;
we omit universe levels for conciseness.
